The Three-HITs Theorem

### 2017-05-13 Paper/Paper.tex
Added new files to project

%% Please provide for each author the \author and \affil macro, even when authors have the same affiliation, i.e. for each author there needs to be the  \author and \affil macros
\author[1]{Andrej Bauer\thanks{
The author acknowledges the financial support from the Slovenian Research Agency (research core funding No.~P1-0294) at Institute of Mathematics, Physics and Mechanics, Ljubljana, Slovenia. This material is based upon work supported by the Air Force Office of Scientific Research, Air Force Materiel Command, USAF under Award No.~FA9550-14-1-0096.}}
\author[2]{Niels van der Weide\thanks{This work was partially supported by EU COST Action Eutypes (CA15123).}}
\affil[1]{University of Ljubljana, Slovenia\\
  \texttt{Andrej.Bauer@andrej.com}}
\affil[2]{Department of Computer Science, Radboud University, Nijmegen, The Netherlands\\
  \texttt{nweide@cs.ru.nl}}
\authorrunning{A.\ Bauer and N.\ van der Weide} %mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et. al.'

@@

\begin{definition}
Let $A, B$ be types, let $f, g : A \rightarrow B$ be maps, and let $x : A$ be a point of $A$.
Then for all $e : f = g$ we define a path $e \fpath x : f \> x = g \> x$ using path induction which sends $\refl$ to $\refl$.
\end{definition}

>>>>

%% Please provide for each author the \author and \affil macro, even when authors have the same affiliation, i.e. for each author there needs to be the  \author and \affil macros
\author[1]{Andrej Bauer\thanks{
The author acknowledges the financial support from the Slovenian Research Agency (research core funding No.~P1-0294) at Institute of Mathematics, Physics and Mechanics, Ljubljana, Slovenia. This material is based upon work supported by the Air Force Office of Scientific Research, Air Force Materiel Command, USAF under Award No.~FA9550-14-1-0096.}}
\author[2]{Niels van der Weide\thanks{This work was partially supported by EU COST Action Eutypes (CA15123).}}
\affil[1]{University of Ljubljana, Slovenia\\
  \texttt{Andrej.Bauer@andrej.com}}
\affil[2]{iCIS, Radboud University, Nijmegen, The Netherlands\\
  \texttt{nweide@cs.ru.nl}}
\authorrunning{A.\ Bauer and N.\ van der Weide} %mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et. al.'

@@

\begin{definition}
\label{def:ap_ext_pt}
Let $A, B$ be types, let $f, g : A \rightarrow B$ be maps, and let $x : A$ be a point of $A$.
Then for all $e : f = g$ we define a path $e \fpath x : f \> x = g \> x$ using path induction which sends $\refl$ to $\refl$.
\end{definition}
